### 2019-05-16 doc/bilevel/paper.tex
updates to bilevel

The \code{pyomo.bilevel} package uses the \code{SubModel} component to declare a block that defines a lower-level problem. 
For example, consider:
\begin{qlisting}
model = ConcreteModel()
model.x = Var(bounds=(1,2))
model.v = Var(bounds=(1,2))
model.sub = SubModel()
model.sub.y = Var(bounds=(1,2))
model.sub.w = Var(bounds=(-1,1))

model.o = Objective(expr=model.x + model.sub.y + model.v)
model.c = Constraint(expr=model.x + model.v >= 1.5)
model.sub.o = Objective(expr=model.x+model.sub.w, sense=maximize)
model.sub.c = Constraint(expr=model.sub.y + model.sub.w <= 2.5)
\end{qlisting}
This Pyomo model defines four variables, \code{x}, \code{v}, \code{sub.y} and \code{sub.w}.
Variables \code{x} and \code{v} are declared in the upper-level
problem, and \code{v} only appears in the upper-level problem.
Variables \code{sub.y} and \code{sub.w} are declared in the submodel.
However, note that the \code{sub.y} variable appears in the upper-level
problem, while the \code{sub.w} variable only appears in the
lower-level problem.

While this syntax mimics the structure of (\ref{eqn:bilevel-compact}), it adds additional abstractions that make it difficult to interpret:
\begin{itemize}

>>>>

\subsection{Introduction to \code{pao}}

The Python package \code{pao} is a bilevel mathematical programming library that has dependencies on \code{pyomo} for syntactical representation of bilevel problems. Similar to \code{pyomo} mathematical problems, \code{pao} problems can be optimized with solvers that are written either in Python or in compiled, low-level languages.

The \code{pao} package uses the \code{SubModel} component in \code{pyomo} to declare a block that defines a lower-level problem. 
For example, consider the bilevel problem:
\begin{equation}
\label{eqn:bilevel_ex1}
\begin{array}{ll}
\min_{v \in [1,2], x \in [1,2]}   & v + x + y\\
\st                 & x + v \geq 1.5\\
                    & y \in P(v,x)
\end{array}
\end{equation}
where 
\[
\begin{array}{llll}
P(v,x) & = & \argmin_{w \in [-1,1], y \in [1,2]}    & x + w\\
 & &                            &  y + w \leq 2.5
\end{array}
\]
which can be represented in \code{pao} as:

\begin{qlisting}
model = ConcreteModel()
model.x = Var(bounds=(1,2))
model.v = Var(bounds=(1,2))
model.sub = SubModel()
model.sub.y = Var(bounds=(1,2))
model.sub.w = Var(bounds=(-1,1))

model.o = Objective(expr=model.x + model.sub.y + model.v, sense=minimize)
model.c = Constraint(expr=model.x + model.v >= 1.5)
model.sub.o = Objective(expr=model.x+model.sub.w, sense=maximize)
model.sub.c = Constraint(expr=model.sub.y + model.sub.w <= 2.5)
\end{qlisting}
This Pyomo model defines four variables, \code{x}, \code{v}, \code{sub.y} and \code{sub.w}.
Variables \code{x} and \code{v} are declared in the upper-level
problem, and \code{v} only appears in the upper-level problem.
Variables \code{sub.y} and \code{sub.w} are declared in the submodel.
However, note that the \code{sub.y} variable appears in the upper-level
problem, while the \code{sub.w} variable only appears in the
lower-level problem.

While this syntax mimics the abstract structure of \eqref{eqn:bilevel-compact} -- as represented directly in \eqref{eqn:bilevel_ex1} --  it adds additional abstractions that make it difficult to interpret:
\begin{itemize}
